---
title: "Cardscount"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cardscount}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Cardscount)
```

## Introduction


This vignette provides an overview of the `Cardscount` package, which provides functions for working to calculate the score on hand of the player and dealer in a blackjack game. It includes one main function, `play_blackjack`, which calculates the score of a hand in blackjack based on the numeric value of the cards and the rules of the game.

## Installation

You can install `Cardscount` from CRAN using the following command:


```{r warning=FALSE, eval=FALSE}
install.packages("Cardscount")
```

or through GitHub using the following command:

```{r warning=FALSE, eval=FALSE}
devtools::install_github("phunghai-phan/Cardscount")
```

## How to load the package
You can load "Cardscount" by using this following command:

```{r warning=FALSE, eval=FALSE}

library("Cardscount")
```

## Basic Usage
### Function: calculate_blackjack_score

This function calculates the score of a hand in blackjack based on the provided cards.

*Parameters:*

 "cards": A list of strings representing the cards in the hand. Each string is a two-character string where the first character is the value of the card and the second character is the suit of the card. The card values are as follows:
- Number cards are their value (2 through 10).

- Jack, Queen, and King (face cards) are all valued at 10.

- Aces are valued at 11 if the total score of the hand is less than or equal to 21, and 1 otherwise.

*Returns:*

A list of player scores and the dealer's score.

```{r message=FALSE, eval=FALSE}
# Example usage:
library(Cardscount)
 play_blackjack()

# On console, you will see:
Enter the number of players: 1
Dealer, enter your cards (comma-separated): 
Q,A
Enter cards for Player  1  (comma-separated): 
10,9
Player  1  score:  19 
Dealer score:  21 
```

## Conclusion

This vignette provided a brief overview of the "Cardscount" package and its calculate_blackjack_score function. Explore the documentation and experiment with the function to calculate blackjack scores effectively.
